Simulating the Lipkin-Meshov-Glikov model on a classical computer

### 2023-05-30 doc/paper.tex
Small fix, and finished result description for result of quantum circuits
Signed-off-by: Gregz9 <gregorkajda@gmail.com>

\begin{enumerate}
	\item[\textbf{I}.] \textbf{Identity gate} \\
		This gate does nothing to the state of the qubit, as if a gate never was applied to the qubit in the first place.
		\begin{equation*}
			I = \begin{pmatrix}
			1 & 0 \\
			0 & 1 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{II.}] \textbf{Pauli-X gate} \\
		The Pauli-X gate, also known as the quantum NOT-gate, flips the probability amplitudes $\alpha$ and $\beta$, meaning that these values swap place in the state vector. 
		\begin{equation*}
			X = \begin{pmatrix}
			0 & 1 \\
			1 & 0 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{III.}] \textbf{Pauli-Y gate} \\
		The action of the Pauli Y gate can be described as the mapping of $|0>$ to $i|1>$ and $|1>$ to $i¦0>$. The action of the gate can also be viewed as a rotation of the state of the qubit around the y-axis of the Bloch sphere by 180 degrees.
		\begin{equation*}
			Y = \begin{pmatrix}
			0 & -i \\
			i & 0 \\
		\end{pmatrix}.
	\end{equation*}

	\item[\textbf{IV.}] \textbf{Pauli-Z gate} \\
		The Pauli Z gate flips the phase of $|1>$ to $-|1>$ while leaving $|0>$, meaning it flips the relative phase of the qubit. 
		\begin{equation*}
			Z = \begin{pmatrix}
			1 & 0 \\
			0 & -1 \\
		\end{pmatrix}.
	\end{equation*}

@@

@@

		\begin{equation*}
			S = \begin{pmatrix}
			1 & 0 \\
			0 & i \\
		\end{pmatrix}.
	\end{equation*}
		For a single qubit, application of each of these matrices represents a rotation of the qubit on the \textit{Bloch sphere (Fig. 1)}. (For more details, take a look at [Hundt, p.56] or [Nielsen, p.19])

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.3\textwidth]{Bloch_sphere.svg.png}
  \caption{Caption text describing the picture.}
  \label{fig:example}
\end{figure}

@@

\subsection{Application of quantum gates to single qubits basis states}

As the first step of our project, we prepared single qubits in their basis state $|0>$ and $|1>$ and studied the result the application of the various quantum gates had on these one qubit systems. The effect each gate had on the basis states is presented below in the order the gates were listed in \textbf{Section II}. The results of applying the gates are:

		\begin{enumerate}
			\item[\textbf{I}. ] Identity gate \\
				The result of applying both the $\sigma_0$ gate to both $|0>$ and $|1>$ results in the exact same states, as the identity gate is simply the identity matrix. Presented using matrices and vectors, the results can be written.
				\[
				I \begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				1 & 0 \\
				0 & 1
				\end{pmatrix} \\ \\ \\
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				\]
			\item[\textbf{II}. ] Pauli-X gate \\
				The application of the Pauli X gate result in flipping of the probability amplitudes of the qubit, resulting in $\alpha$ and $\beta$ swapping places in the qubit. 
				\[
				I \begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				0 & 1 \\
				1 & 0
				\end{pmatrix} \\ \\ \\
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				\beta \\
				\alpha
				\end{pmatrix}
				\] 
			\item[\textbf{III}. ] Pauli-Y gate \\
				The application of the Y-gate resulted in the exact behavipur described in point III of \textbf{Section II: Quantum gates}, a rotation of the qubits amplitudes bu 180 degrees around the y-axis. The result presented as a matrix-vector product is: 
				\[
				Y \begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				0 & -i \\
				i & 0
				\end{pmatrix}
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				-i\beta \\
				i\alpha
				\end{pmatrix}
				\] 	
			\item[\textbf{VI}. ] Pauli-Z gate \\
				Just as expected based on the description provieded in the theory part, the Z-gate flips the relative phase of the state vector of our qubit. The result visualized using matrix-vector product is
				\[
				Z \begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				1 & 0 \\
				0 & -1
				\end{pmatrix}
				\begin{pmatrix}
				\alpha \\
				\beta
				\end{pmatrix}
				=
				\begin{pmatrix}
				\alpha \\
				-\beta
				\end{pmatrix}
				\]
			\item[\textbf{VI}. ] Pauli-Z gate \\

>>>>

\begin{enumerate}
	\item[\textbf{I}.] \textbf{Identity gate} \\
		This gate does nothing to the state of the qubit, as if a gate never was applied to the qubit in the first place. Presented below is the matrix representation of the quantum gate the result of applying it to a single qubit:
		\begin{equation*}
			I = \begin{pmatrix}
			1 & 0 \\
			0 & 1 \\
		\end{pmatrix}.
		\end{equation*}

		\begin{equation*}
		H \begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		=
		\begin{pmatrix}
		1 & 0 \\
		0 & 1
		\end{pmatrix}
		\begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		=
		\begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		\end{equation*}

	\item[\textbf{II.}] \textbf{Pauli-X gate} \\
		The Pauli-X gate, also known as the quantum NOT-gate, flips the probability amplitudes $\alpha$ and $\beta$, meaning that these values swap place in the state vector. Presented below is the matrix representation of the quantum gate the result of applying it to a single qubit:
		\begin{equation*}
			X = \begin{pmatrix}
			0 & 1 \\
			1 & 0 \\
		\end{pmatrix}.
	\end{equation*}

	\begin{equation*}
		H \begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		=
		\begin{pmatrix}
		1 & 1 \\
		1 & -1
		\end{pmatrix}
		\begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		=
		\begin{pmatrix}
		\beta \\
		\alpha
		\end{pmatrix}
	\end{equation*}

	\item[\textbf{III.}] \textbf{Pauli-Y gate} \\
		The action of the Pauli Y gate can be described as the mapping of $|0>$ to $i|1>$ and $|1>$ to $i¦0>$. The action of the gate can also be viewed as a rotation of the state of the qubit around the y-axis of the Bloch sphere by 180 degrees. Presented below is the matrix representation of the quantum gate the result of applying it to a single qubit:

		\begin{equation*}
			Y = \begin{pmatrix}
			0 & -i \\
			i & 0 \\
		\end{pmatrix}.
	\end{equation*}

	\begin{equation*}
		H \begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		=
		\frac{1}{\sqrt{2}}\begin{pmatrix}
		0 & -i \\
		i & 0
		\end{pmatrix}
		\begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		=
		\frac{1}{\sqrt{2}}\begin{pmatrix}
		-i\beta \\
		i\alpha
		\end{pmatrix}
	\end{equation*}

	\item[\textbf{IV.}] \textbf{Pauli-Z gate} \\
		The Pauli Z gate flips the phase of $|1>$ to $-|1>$ while leaving $|0>$, meaning it flips the relative phase of the qubit. Presented below is the matrix representation of the quantum gate the result of applying it to a single qubit:

		\begin{equation*}
			Z = \begin{pmatrix}
			1 & 0 \\
			0 & -1 \\
		\end{pmatrix}.
	\end{equation*}

		\begin{equation*}
			Z \begin{pmatrix}
			\alpha \\
			\beta
			\end{pmatrix}
			=
			\begin{pmatrix}
			1 & 0 \\
			0 & -1
			\end{pmatrix}
			\begin{pmatrix}
			\alpha \\
			\beta
			\end{pmatrix}
			=
			\begin{pmatrix}
			\alpha \\
			-\beta
			\end{pmatrix}
	\end{equation*}

@@

		\begin{equation*}
			H \begin{pmatrix}
			\alpha \\
			\beta
			\end{pmatrix}
			=
			\frac{1}{\sqrt{2}}\begin{pmatrix}
			1 & 1 \\
			1 & -1
			\end{pmatrix}
			\begin{pmatrix}
			\alpha \\
			\beta
			\end{pmatrix}
			=
			\frac{1}{\sqrt{2}}\begin{pmatrix}
			\alpha + \beta \\
			\alpha - \beta
			\end{pmatrix}
	\end{equation*}

@@

		\begin{equation*}
			S = \begin{pmatrix}
			1 & 0 \\
			0 & i \\
		\end{pmatrix}.
	\end{equation*}

	\begin{equation*}
		S \begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		=
		\begin{pmatrix}
		1 & 0 \\
		0 & i
		\end{pmatrix}
		\begin{pmatrix}
		\alpha \\
		\beta
		\end{pmatrix}
		=
		\begin{pmatrix}
		\alpha \\
		i\beta
		\end{pmatrix}
	\end{equation*}

	For a single qubit, application of each of these matrices represents a rotation of the qubit on the \textit{Bloch sphere (Fig. 1)}. (For more details, take a look at [Hundt, p.56] or [Nielsen, p.19])

\begin{figure}[H]
  \centering
  \includegraphics[width=0.3\textwidth]{Bloch_sphere.svg.png}
  \caption{Three dimensional sphere, known as the Bloch sphere, used to visualize the state of a qubit and the action each quantum gate has on the state vector of the qubit.}
  \label{fig:example}
\end{figure}

@@

\subsection{Application of quantum gates to single qubits basis states}
In the initial phase of our project, we embarked on the exploration of single qubits by preparing them in their respective basis states $|0\rangle$ and $|1\rangle$. Our objective was to investigate the effects of different quantum gates on these individual qubit systems. Notably, the outcomes observed align precisely with the theoretical predictions discussed in the earlier sections of this report. Therefore, we present the resulting states obtained by applying these gates to a qubit prepared in the state $|0\rangle$ in the table below, which serves as a comprehensive overview of our experimental findings.

\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|}
\hline
Initial State & Quantum Gate & Final State \\
\hline
$\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ & $I = \begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix}$ & $\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ \\
\hline
$\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ & $X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}$ & $\begin{pmatrix} 0 \\ 1 \end{pmatrix}$ \\
\hline
$\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ & $Y = \begin{pmatrix} 0 & -i \\ i & 0 \end{pmatrix}$ & $i\begin{pmatrix} 0 \\ 1 \end{pmatrix}$ \\
\hline
$\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ & $Z = \begin{pmatrix} 1 & 0 \\ 0 & -1 \end{pmatrix}$ & $\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ \\
\hline
$\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ & $H = \frac{1}{\sqrt{2}}\begin{pmatrix} 1 & 1 \\ 1 & -1 \end{pmatrix}$ & $\frac{1}{\sqrt{2}}\begin{pmatrix} 1 \\ 1 \end{pmatrix}$ \\
\hline
$\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ & $S = \begin{pmatrix} 1 & 0 \\ 0 & i \end{pmatrix}$ & $\begin{pmatrix} 1 \\ 0 \end{pmatrix}$ \\
\hline
\end{tabular}
\captionof{table}{Results of applying listed gates to a qubit prepared in the basis state $|0\rangle$.}
\end{center}

As part of our expermients with quantum circuits, we also constructed the entangler circuit and prepared the first bell state $\frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)$. Thereafter we applied the Hadamard gate to first and second gates separetly, before proceeding with the application of CNOT(0,1)-gate, and ending with the application of the Hadamard and CNOT(0,1) gates in the reverse order to that of the entangler circuit. The last operation resulted in the uncomputation of the entanglement. All results are presented in the table below.

\begin{center}
\begin{tabular}{|c|c|c|}
\hline
First Bell Pair & Quantum Operators & Resulting State \\
\hline
$\frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)$ & $H \otimes I$ & $\frac{1}{\sqrt{2}}(|00\rangle + |10\rangle + |01\rangle + |11\rangle)$ \\
$\frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)$ & $I \otimes H$ & $\frac{1}{\sqrt{2}}(|00\rangle + |10\rangle + |01\rangle + |11\rangle)$ \\
$\frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)$ & CNOT(0,1) & $\frac{1}{\sqrt{2}}(|00\rangle + |01\rangle)$ \\
$\frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)$ & $H \otimes$ CNOT(0,1) & $|00\rangle$ \\
$\frac{1}{\sqrt{2}}(|00\rangle + |11\rangle)$ & CNOT(0,1)adj$\otimes$Hadj & $|00\rangle$ \\
\hline
\end{tabular}
\end{center}

\subsection{Solving the ine qubit synthetic Hamiltonian}
